Secure Composition of Robust and Optimising Compilers

### 2023-07-06 popl/main.tex
Add conclusion and acks

In order to define secure compilers one needs programming languages.
To this end, this section defines the languages $\Ltms$, $\Ltrg$, $\Lms$, and $\Lscct$.
In this paper, $\Ltms$ is the only statically typed language and exhibits the property that all well-typed programs are \gls{tms}.
However, one can still write and evaluate $\Ltms$ programs that are well-typed, but perform out-of-bounds memory accesses, so the language is not \gls{sms}.
In contrast, $\Ltrg$ is untyped and does not provide any guarantees with regards to \gls{ms}.
$\Lms$ is exactly the same language as $\Ltrg$, but this paper still distinguishes the two for sake of readability.
For all these languages, so $\Ltms$, $\Ltrg$, and $\Lms$, programmers assume \gls{cct} to hold, because the compiler is said to ensure it, similarily to what is being done in literature~\cite{cauligi2019fact}.
This assumption does not hold anymore for the language $\Lscct$, which leaks information on branches and binary operations.
But, contrary to the other languages, one can read and write to a model-specific register indicating a ``\gls{cct}-mode''.

>>>>

This section defines programming languages that the secure compilers defined in the next section will make use of.
To this end, this section defines the languages $\Ltms$, $\Ltrg$, $\Lms$, and $\Lscct$.
In this paper, $\Ltms$ is the only statically typed language and exhibits the property that all well-typed programs are \gls{tms}.
However, $\Ltms$ programs are not \gls{sms}.
That is, there are well--typed $\Ltms$ programs that perform an out--of--bounds access.
In contrast, $\Ltrg$ is untyped and does not provide any guarantees with regards to \gls{ms}.
$\Lms$ is exactly the same language as $\Ltrg$, but this paper still distinguishes the two for sake of readability.
All three languages --- so $\Ltms$, $\Ltrg$, and $\Lms$ --- assume \gls{cct} to hold.
Even though it is possible to write programs that, e.g., return early in loops, which is trivially not \gls{cct}, they can be transformed to adhere to \gls{cct}~\cite{cauligi2019fact}.
The language $\Lscct$ allows violating \gls{cct} by emitting events on, e.g., branching and division, that contain secrets.
As a countermeasure, the language provides a way to read and write to a {\em model--specific register} that enables a ``\gls{cct}-mode''.
